Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Create preprocessing.Rmd
Update preprocessing.Rmd

---
title: "checkData"
output: html_document
date: "2023-08-21"
---

@@

# Remove non-relevant rows

## Remove pilot journals

Removing all rows that were entered during piloting and therefore not part of the main sample.

```{r}
d_journals <- d_journals %>%
  filter(pilot == "No") %>%
  select(-pilot)
```

>>>>

---
title: "Preprocessing"
output: html_document
date: "2023-08-21"
---

@@
